Towards Compiler-Agnostic Performance in Finite-Difference Codes. (TBC)

### 2014-11-10 shallow_perf.tex
Starting to draft the steps taken in the serial work

\subsubsection{Subsubsection Heading Here}
Subsubsection text here.

@@

>>>>

\subsection{The {PS}y{KA}l Approach}
Proliferation of lightweight cores is resulting in increased
complexity in the programming models required to achieve performance.
Combine with the complexity of e.g. a model simulating circulation in
the global ocean. Significant challenge in software engineering.
Propose an approach for meeting this challenge by separating the
computational science demands from the e.g. oceanographic demands.

\begin{figure}
\centering
\caption{The {PS}y{KA}l Approach.}
\end{figure}

While encapsulation makes it easier to produce more robust software,
it can often come with a performance penalty. In this work we
investigate the origin of this penalty and the steps required to
remove it.

@@

\begin{itemize}

\item Performance of the 'original' version of shallow; i.e. the version we
were supplied with at the start of this work.

\item Performance of the vanilla, unoptimised version after it has been
re-structured following the {PS}y{KA}l approach.

\end{itemize}
